% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod,
  oneside]{scrartcl}
\usepackage{xcolor}
\usepackage[left=1in,marginparwidth=2.0666666666667in,textwidth=4.1333333333333in,marginparsep=0.3in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


% \documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
% \usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
% \usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
% \hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
% \addbibresource{citations.bib}
% \setlength\bibitemsep{1em}

\usepackage[colorlinks = true,
            linkcolor = linkcolour,
            urlcolor  = linkcolour,
            citecolor = linkcolour,
            anchorcolor = linkcolour]{hyperref}

\newcommand{\MYhref}[3][black]{\href{#2}{\color{#1}{#3}}}%

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Jinming Ren} \\[7.5pt]
\href{https://github.com/marcobisky}{\raisebox{-0.05\height}\faGithub\ marcobisky} \ $|$ \ 
% \href{https://linkedin.com/in/username}{\raisebox{-0.05\height}\faLinkedin\ username} \ $|$ \ 
\href{https://marcobisky.moe}{\raisebox{-0.05\height}\faGlobe \ marcobisky.moe} \ $|$ \ 
\href{mailto:marcobisky@outlook.com}{\raisebox{-0.05\height}\faEnvelope \ marcobisky@outlook.com} \ $|$ \ 
\href{tel:+86 17882004164}{\raisebox{-0.05\height}\faMobile \ +86 17882004164} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Experience
\section{Education}


\textbf{University of Electronic Science and Technology of China (UESTC)}  \hfill Sept 2022 --- Present

\textbf{University of Glasgow, Dual Degree Program} \hfill Sept 2022 --- Present

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item \textbf{Major}: Electronic and Computer Engineering; \MYhref{https://marcobisky.moe/cv/score.pdf}{GPA: 3.87/4.0, Ranking: 2/164 (Top 1\%).} 
    \item \textbf{Relevant Coursework}: Signals and Systems, Stochastic Processes, Artificial Intelligence and Machine Learning, Information Theory, Electrodynamics, Digital Circuit Design, etc.
    \item \textbf{Online Course}: Abstract Algebra, Complex Analysis, Differential Geometry, Control Theory, etc.
\end{itemize}


\section{Research}

\textbf{GAT-based Multi-Task RL for Robust PVT-Aware Analog Design} \hfill Ongoing


\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Proposed a GAT-based multi-task Reinforcement Learning framework to optimize analog circuits under diverse PVT corners.
    \item Modeled PVT conditions as graph nodes, enabling adaptive attention to corner-specific bottlenecks.
    \item Reduced specific violations by $19\times$ and simulations by 69\% on \texttt{AnalogGym} benchmarks.
\end{itemize}


\MYhref{https://marcobisky.moe/tinyml/}{\textbf{System-level Co-Design of RISCV Accelerators for TinyML at the Edge}} \hfill Ongoing

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Designing and implementing hardware-accelerated TinyML kernels that are adaptable and efficient for edge computing using \texttt{Chisel}, \texttt{Verilog}, \texttt{Python} and \texttt{C++}.
    \item Exploring a large multi-dimensional design space using automated methods (e.g.  heuristic and evolutionary algorithms) to identify optimal configurations balancing accuracy, energy, and latency.
    \item Conducted under the supervision of \href{https://scholar.google.com/citations?user=1NT1jFMAAAAJ&hl=en}{Prof. Yun Li}.
\end{itemize}


% \MYhref{https://marcobisky.moe/cv/physics-paper.pdf}{\textbf{Generalized Fields and Extension to Higher Dimensions}} \hfill Oct 2023 --- Feb 2024

% \begin{itemize}
%     \setlength\itemsep{-0.5em}
%     \item Investigated generalized natural fields and behaviors in higher dimensions,  Supervised by \href{https://scholar.google.com/citations?user=Amwv33EAAAAJ&hl=en}{Prof. Yidong Liu}.
%     \item  Provided an alternative perspective of understanding the electric field generated by a charged object by extending it to higher dimensions, making some symmetries in electrostatics much more tangible.
% \end{itemize}

\textbf{Movable Antenna (MA) for Anti-jamming} \hfill Feb 2025 --- Jun 2025

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Conducted a heuristic investigation into Anti-jamming through stochastic antenna movement under the supervision of \href{https://scholar.google.com.sg/citations?user=JtHltIoAAAAJ&hl=en-EN}{Prof. Weidong Mei}.
\end{itemize}

\section{Projects}



\textbf{\MYhref{https://marcobisky.moe/posts/quadrocopter-control/}{Control} and \MYhref{https://marcobisky.moe/cv/drone-cv.pdf}{Computer Vision} for \MYhref{https://marcobisky.moe/cv/drone.pdf}{Autonomous Quadcopter System}} \hfill Feb 2025 --- Jun 2025

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Developed an automatic quadrotor aircraft for objection detection, route planning, and closed-loop flight control.
    \item Used \texttt{ROS2} and \texttt{OpenCV} library to implement originally designed computer vision algorithms for real-time landing area detection.
\end{itemize}

\MYhref{https://github.com/Marcobisky/my-riscv}{\textbf{Visual RV32I CPU Core}} \hfill Jan 2025 --- Mar 2025

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Designed and simulated an entire RISCV 32-bit CPU from scratch in \texttt{Digital} Software for visualization of working principle.
    \item Supported basic peripherals: GPIOs, IIC, UART, etc.
    \item Implemented a simple boot ROM in assembly, minimal interrupt service for running a Linux kernel.
\end{itemize}


\MYhref{https://github.com/Marcobisky/ame-entropy-source-coding}{\textbf{Adaptive Markov Entropy Source Encoding}} \hfill Oct 2024 --- Nov 2024

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Originally-designed the second-order Markov Adaptive Encoding (AME) to perform source coding of \textit{the Game of Thrones} using \texttt{Python} and \texttt{Matlab}.
    \item Evaluated and compared the performance of AME, Huffman and Fano coding.
\end{itemize}


\MYhref{https://github.com/Marcobisky/CNN-for-mbed}{\textbf{CNN for Embedded Systems}} \hfill Feb 2024 --- May 2024

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Integrated a convolutional neural network (CNN) into an MCU using \texttt{C} in \texttt{MbedOS}.
    \item Enabled smart fall detection, body temperature monitoring and real-time data visualization for patients.
\end{itemize}





\textbf{Human Voice Recognition Smart Car} \hfill Sept 2023 --- Dec 2023

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Designed and implemented a voice-controlled car on STM32F103 using C standard libraries, supporting actions such as moving forwards/backwards, turning/sliding left/right.
    \item Led a 4-member team in the project.
\end{itemize}

\textbf{Digital Door Lock for Dormitory} \hfill Sept 2023 --- Oct 2023

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Designed and implemented an embedded digital door lock system in \texttt{C++} on Nucleo L432KC MCU. 
    \item Developed basic functions include manually setting up password, automatically lock for repeated wrong passwords, OLED message displaying, etc.
    \item Led a 3-member team in the project.
\end{itemize}


\textbf{First Place in ``XinTong Cup" Electronic Design Competition} \hfill Sept 2022 --- Oct 2022

\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item Designed and implemented a 8-key music player using register-based development in \texttt{Keil C51} on STC89C52 MCU.
    \item Developed functions includes single note/chord playing, recording, replay and rewind capability, etc.
\end{itemize}



\section{Relevant Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{IT Skills} &  \normalsize{Latex, Quarto Markdown, Typst, \MYhref{https://www.bilibili.com/video/BV1AterevErt/?spm_id_from=333.1387.homepage.video_card.click&vd_source=42579e22289b6144ba0b2bdcf99834e3}{Manim}, \MYhref{https://github.com/Marcobisky}{Github}, Microsoft Office.}\\
\textbf{Programming} &  \normalsize{\texttt{C/C++}, \texttt{Python}, \texttt{Matlab}, \texttt{Verilog}, \texttt{Chisel}, \texttt{RISCV Assembly}.} \\  
\textbf{Language} &  \normalsize{Native Chinese, Fluent English.} \\
\end{tabularx}


\section{Awards}

\textbf{Top Academic Scholarship of UESTC (Top 5\%)} \hfill Dec 2023, Dec 2024

\textbf{China National Scholarship (Top 3\%)} \hfill Dec 2024

\MYhref{http://www.moe.gov.cn/srcsite/A17/moe_794/moe_628/202408/t20240806_1144389.html}{\textbf{First Prize: 7th National College Art Exhibition and Performance}} \hfill Sept 2024



\vfill
\center{\footnotesize Last updated: \today}

\end{document}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{sidenotes}{}{\usepackage{sidenotes}}
\@ifpackageloaded{marginnote}{}{\usepackage{marginnote}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\author{}
\date{}
\begin{document}







\end{document}
